TUD Datasets: A collection of benchmark datasets for learning with graphs

### 2020-03-26 main.tex
MC.

\subsection{Evaluation tools}

@@

@@

>>>>

\subsection{Evaluation tools}\label{eval}

@@

Our intention here is to investigate the benefits XXXX. More precisely, we address the following questions:
\begin{description}
	\item[Q1] dfgkposdk
	\item[Q2] dfdsfsdd
	\item[Q3] sdfsdfsdfsdfdssdf
\end{description}

@@

Describe kernel, gnns used

\paragraph{Datasets.}

\paragraph{Graph kernels.}

\paragraph{GNNs.}

We used the evaluation procedute described in~\cref{eval}, describe used hyperparamter

\subsection{Results and discussion}

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcccccc@{}}	\toprule

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Graph Kernel}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Data0}}         &  {\textsc{Data1}}      & {\textsc{Data1}}           & {\textsc{Data1}}       & {\textsc{Data1}}           & {\textsc{Data1}}      \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
				& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
			\cmidrule{2-8}	
			\multirow{4}{*}{\rotatebox{90}{GNN}}	& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
		& \text{1-WL}            &    \scriptsize $\pm $       & \scriptsize $\pm $ & \scriptsize $\pm $ &  \scriptsize $\pm $ & \scriptsize $\pm $ & \scriptsize $\pm $ \\
			\bottomrule
	\end{tabular}}
\end{table*}
